\problemname{Pub Crawl}

Fritjof is going to his first ever pub crawl. Since he doesn't want to go all out on his very first
time, he's decided that he's only going to visit a single pub. As he likes all pubs equally much he
will stay at the pub for an equal amount of time regardless of which pub it is. To still be able to
brag about the amount of time he's been on the pub crawl, he wants to visit the pub with the longest
queue time. Which pub should Fritjof go to?

\section*{Input}

The first line of input contains an integer $N$ ($1 \leq N \leq 10^5$), the number of pubs Fritjof
can choose between. The $i$th of the following $N$ lines contains the name of the $i$th pub $p_i$, the number of
people in the queue $k_i$ ($0 \leq k_i \leq 10^4$) and the integer time $t_i$ it takes for each person to get in
($1 \leq t_i \leq 10^4$).

Each $p_i$ is between $1$ and $10$ characters long and only consists of lowercase and uppercase
alphabetical characters (a-z and A-Z). All pub names are unique.

\section*{Output}

Print one line with the name of the pub with the longest queue time and the total
time it would take for Fritjof to enter the pub. If there are multiple pubs with the same queue time,
print the first suitable pub in the list.

\section*{Explanation of Sample 1}

The last two people in the queues for Gasquen and JAPripps will both enter at time $100$. But it would
then take an additional $5$ and $20$ minutes until Fritjof could enter the pubs if he stood in their
respective queues. To maximize the time spent queuing, Fritjof should queue for JAPripps for a total
of $120$ minutes.
