\problemname{Gasqutvå}

Gasquen is antiquated so Gasqutvå shall now be crowdfunded by the Chalmers students.
The $N$ students communicate along a tree where the students are nodes. Students are arbitrarily numbered from $1$ to $N$.
The $i$th student's generosity is described by one integer $a_i$.
You are to choose the first student to donate to the campaign, who will begin by donating $100$ kr and then tell their neighbours in the tree about the campaign.
When a student $i$ tells a neighbour $j$ about the campaign, and student $j$ hasn't already donated, they will donate $d_j=d_i+a_j$ kr where $d_i$ is the amount $i$ donated.
Student $j$ will then go on to tell their neighbours in the tree about the campaign.
Which student should donate first to maximize the total amount raised?

\section*{Input}

The first line of input contains one integer $2 \leq N$, the number of students in the tree.
Each of the following $N$ lines contains one integer $0 \leq a_i \leq 10^9$ describing how generous the $i$th student is.
After that, each of the following $N-1$ lines contains two integers $1\leq i, j \leq N$ denoting that students $i$ and $j$ are neighbours in the tree.
It is guaranteed that the connections form a tree.

\section*{Output}

Print the number of the student that should donate first to maximize the total amount raised. If there are multiple suitable students, choose the one with the lowest number.

\section*{Scoring}

Your solution will be tested on a set of test groups, each worth a number of points. To get the
points for a test group you need to solve all test cases in the test group. Your final score will be
the maximum score of a single submission.

\noindent
\begin{tabular}{| l | l | l |}
\hline
Group & Points     & Constraints \\ \hline
$1$   & $60$       & $N \leq 100$ \\ \hline
$2$   & $40$       & $N \leq 10^5$ \\ \hline
\end{tabular}
